Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-05-22 main.tex
updated figure 4.  code to change it is in results/random_data/bench_PALM1_paper1.m deleted bad experiments

The first experiment compares the performance of our two proposed
implementations of the general $\ell_1$-min (Algorithm \eqref{alg:alm}) given a
generic random matrix $A$ and a random sparse vector $\xx_0$.  The measurement
$d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each
entry randomly generated from the standard normal and normalized with unit
column norm.  The ratio of $d:n$ varied from $1:10$ to $5:10$ with $n$ varying
from 500 to 8000.  The ground truth signals, $\xx_0$ had a sparsity rate of 0.1
with elements generated using the standard normal and also normalized with unit
norm.  Because the ground truth signal $\xx_0$ was known, the algorithm
terminated when $\|\bx-\bx_0\| < \tau$.  The measurement vector was generated
with the equation $\bb_0 = A \xx_0$.

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The x-axis represents the size of the $A$ matrix and the y-axis represents the
average amount of time it to complete a single problem instance.  The GPU
implementation tends to be faster than the CPU implementation at solving a
single large problem, whereas the the CPU implementation is faster at solving a
single small problem.  
\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{results/random_data/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of $A$.}
\label{fig:random_data}
\end{figure}

>>>>

The first experiment compares the performance of our two proposed
implementations of the general $\ell_1$-min (Algorithm \eqref{alg:alm}) given a
generic random matrix $A$ and a random sparse vector $\xx_0$.  The measurement
$d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each
entry randomly generated from the standard normal and normalized with unit
column norm.  The ratio of $d/n$ =$1/2$ with $n$ varying
from 1000 to 8000.  The ground truth signals, $\xx_0$ had a sparsity rate of 10\% of d
with elements generated using the standard normal and also normalized with unit
norm.  Because the ground truth signal $\xx_0$ was known, the algorithm
terminated when $\|\bx-\bx_0\| < \tau$ with $\tau=10^{-3}$.  The measurement vector was generated
with the equation $\bb_0 = A \xx_0$.

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The x-axis represents the size of the $A$ matrix and the y-axis represents the
average amount of time it to complete a single problem instance.  The GPU
implementation tends to be faster than the CPU implementation at solving a
single large problem, whereas the the CPU implementation is faster at solving a
single small problem.  
\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figures/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of $A$.}
\label{fig:random_data}
\end{figure}
